### 2022-11-22 manuscript.Rmd

authornote: |
  This work was conducted within the project “Lifespan Rhythms of Memory and Cognition (RHYME)” at the Max Planck Institute for Human Development. ESB is a fellow of the International Max Planck Research School on the Life Course (LIFE; http://www.imprs-life.mpg.de/en). AP is a fellow of the International Max Planck Research School on Computational Methods in Psychiatry and Ageing Research (COMP2PSYCH, https://www.mps-ucl-centre.mpg.de/comp2psych). MW-B received support from the Jacobs Foundation (Early Career Research Fellowship 2017–2019). CTN’s work is supported by a grant from the German Research Foundation (DFG; NG 191/2-1) and an Early Career Research Fellowship by the Jacobs Foundation (2021-1417-99). We are grateful to all members of the RHYME and LIME projects for valuable feedback on the project. Finally, we acknowledge support by the Max Planck Dahlem Campus of Cognition (MPDCC).

@@

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
---

>>>>

authornote: |
  This work was conducted within the project “Lifespan Rhythms of Memory and Cognition (RHYME)” at the Max Planck Institute for Human Development. ESB is a fellow of the International Max Planck Research School on the Life Course (LIFE; http://www.imprs-life.mpg.de/en). AP is a fellow of the International Max Planck Research School on Computational Methods in Psychiatry and Ageing Research (COMP2PSYCH, https://www.mps-ucl-centre.mpg.de/comp2psych). MW-B received support from the Jacobs Foundation (Early Career Research Fellowship 2017–2019). CTN’s work is supported by a grant from the German Research Foundation (DFG; NG 191/2-1) and an Early Career Research Fellowship by the Jacobs Foundation (2021-1417-99). We are grateful to all members of the RHYME and LIME projects for valuable feedback on the project. Finally, we acknowledge support by the Max Planck Dahlem Campus of Cognition (MPDCC).
  The latest supplementary materials for this article are availible at <https://github.com/ebuchberger/Estimating-Power-for-SEM>. The version of code and data used as the basis for this PDF is "`r paste0(repro::current_hash(backend = 'gert'))`".

@@

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
    - aaronpeikert/repro@5a920f7
    - gert
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
---
